---
title: "Object Transport Analysis"
author: "Shanaa Modchalingam"
date: '2023'
output: 
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    
---

```{r setup, include=FALSE, warning=FALSE}
rm(list = ls()) # clean environment

source("../src/helper_funcs.R")
library(data.table)
library(tidyverse)
library(future) # for parallel processing
library(collections)
library(ggbeeswarm)

# Helper functions
##### Helper functions #####
slope <- function(x, y) {
  return(cov(x, y) / var(x))
}

intercept <- function(x, y, slope) {
  b <- mean(y) - (slope * mean(x))
  return(b)
}
```

# Introduction
We are interested in adaptation to visuomotor rotations during the transport of objects to receptacles. Crucially, rotations are mapped to the objects themselves, that is, the perturbation is only applied to a movement while transporting an object. 

In doing so, we are interested in the following questions:
1. Can visual cues (the object) enable object-specific motor memories?
2. Can these object specific motor memories be transferred to the opposite hand (and if so what proportion)?
3. Can people develop multiple object-specific motor memories simultatneously?
4. Do patterns of the above change when learning is more explicit (i.e., through a larger rotation)

# Preliminary Analysis

## Data Import

```{r}
# import data
data_path <- "../data/preprocessed/omnibus/omnibus_bl_corrected.csv"

all_data <- fread(data_path)
```

```{r}
# make any and all summary dfs here
by_trial_df <- all_data %>%
  group_by(exp, type, trial_num) %>%
  summarise(
    mean_obj_angle_3cm_move = mean(obj_angle_3cm_move),
    ci_obj_angle_3cm_move = vector_confint(obj_angle_3cm_move),
    mean_obj_time_start_move = mean(obj_time_start_move),
    ci_obj_time_start_move = vector_confint(obj_time_start_move),
    mean_obj_time_reach = mean(obj_time_reach),
    ci_obj_time_reach = vector_confint(obj_time_reach),
    mean_obj_time_total_move = mean(obj_time_total_move),
    ci_obj_time_total_move = vector_confint(obj_time_total_move),
    mean_hand_angle_3cm_move = mean(hand_angle_3cm_move),
    ci_hand_angle_3cm_move = vector_confint(hand_angle_3cm_move),
    mean_hand_time_start_move = mean(hand_time_start_move),
    ci_hand_time_start_move = vector_confint(hand_time_start_move),
    mean_hand_time_reach = mean(hand_time_reach),
    ci_hand_time_reach = vector_confint(hand_time_reach),
    mean_hand_time_total_move = mean(hand_time_total_move),
    ci_hand_time_total_move = vector_confint(hand_time_total_move),
  )
```

```{r}
# plot obj_angle_3cm_move over trial_num for each ppid
f <- all_data %>%
  ggplot(aes(x = trial_num, y = obj_angle_3cm_move, colour = ppid)) +
  facet_wrap(~exp, ncol = 1) +
  geom_line(alpha = 0.1)

# add in summary data
f <- f + geom_line(data = by_trial_df, aes(x = trial_num, y = mean_obj_angle_3cm_move, colour = type), size = 1.5)

# remove legend
f <- f + theme(legend.position = "none")

f
```
# Dual Rotation Experiments
## Clamp Trials
```{r}
# isolate only the dr_30 and dr_60 data
without_strategy_dr <- all_data %>%
  filter(
    exp %in% c("dr_30", "dr_60"),
    block_num == 13 | block_num == 14
  )

# summarize obj_angle_3cm_move by exp, ppid, obj_shape_sign
clamped_df <- without_strategy_dr %>%
  group_by(exp, ppid, obj_shape_sign) %>%
  summarise(
    mean_obj_angle_3cm_move = mean(obj_angle_3cm_move),
    ci_obj_angle_3cm_move = vector_confint(obj_angle_3cm_move)
  )

clamped_summary_df <- clamped_df %>%
  group_by(exp, obj_shape_sign) %>%
  summarise(
    means = mean(mean_obj_angle_3cm_move),
    cis = vector_confint(mean_obj_angle_3cm_move)
  )
```

```{r}
# plot mean_obj_angle_3cm_move by obj_shape_sign
f <- clamped_df %>%
  ggplot(aes(x = obj_shape_sign, y = mean_obj_angle_3cm_move)) +
  facet_wrap(~exp) +
  geom_beeswarm() +
  geom_point(data = clamped_summary_df, aes(x = obj_shape_sign, y = means), size = 3, colour = "red") +
  geom_errorbar(data = clamped_summary_df, aes(x = obj_shape_sign, y = means, ymin = means - cis, ymax = means + cis), width = 0.2, colour = "red")

f
```

```{r}
# pivot clamped_df wide by obj_shape_sign
clamped_df_wide <- clamped_df %>%
  select(-ci_obj_angle_3cm_move) %>%
  mutate(obj_shape_sign = recode(
    obj_shape_sign,
    "1" = "positive",
    "-1" = "negative"
  )) %>%
  pivot_wider(names_from = obj_shape_sign, values_from = mean_obj_angle_3cm_move) %>%
  mutate(diff = positive - negative)

clamped_df_wide_summary <- clamped_df_wide %>%
  group_by(exp) %>%
  summarise(
    means = mean(diff),
    cis = vector_confint(diff)
  )
```

```{r}
# plot diff
f <- clamped_df_wide %>%
  ggplot(aes(x = exp, y = diff)) +
  geom_beeswarm() +
  geom_point(data = clamped_df_wide_summary, aes(x = exp, y = means), size = 3, colour = "red") +
  geom_errorbar(data = clamped_df_wide_summary, aes(x = exp, y = means, ymin = means - cis, ymax = means + cis), width = 0.2, colour = "red")

f
```


## Rotation Trials

### Per-trial, starting from rotation-switch
```{r}
# isolate only the dr_30 and dr_60 data
rotated_dr <- all_data %>%
  filter(
    exp %in% c("dr_30", "dr_60"),
    type == "reach", dual_rotation != 0
  )

# make a column combining ppid and rotation_switch
rotated_dr <- rotated_dr %>%
  mutate(ppid_miniblock_num = paste0(ppid, "_", miniblock_num))

# plot
f <- rotated_dr %>%
  ggplot(aes(x = trial_in_miniblock, y = obj_angle_3cm_move, colour = miniblock_num)) +
  facet_wrap(~ exp * dual_rotation)

# add lines grouped by ppid
f <- f + geom_line(aes(group = ppid_miniblock_num), alpha = 0.05)

# add horizontal lines at -60, -30, 0, 30, 60
f <- f + geom_hline(yintercept = c(-60, -30, 0, 30, 60), linetype = "dashed", alpha = 0.5)

# set continuous colour scale from red to blue
f <- f + scale_colour_gradient(low = "red", high = "blue")

# save plot
# ggsave("../plots/by_rot_switch.png", f, width = 30, height = 30)

f
```

### Slope and intercept following rotation-switches, vs miniblock_num
```{r}
# isolate only the dr_30 and dr_60 data
rotated_dr <- all_data %>%
  filter(
    exp %in% c("dr_30", "dr_60"),
    type == "reach", dual_rotation != 0
  )

# summarise
rotated_dr_summary <- rotated_dr %>%
  group_by(exp, ppid, miniblock_num, obj_shape_sign) %>%
  summarise(
    slopes = first(obj_angles_when_rot_change_slope),
    intercepts = first(obj_angles_when_rot_change_intercept),
    means = first(obj_angles_when_rot_change)
  )
# multiply slops and intercepts by obj_shape_sign
rotated_dr_summary <- rotated_dr_summary %>%
  mutate(
    slopes = slopes * obj_shape_sign,
    intercepts = intercepts * obj_shape_sign,
    means = means * obj_shape_sign
  )

# make second order summary
rotated_dr_2nd_order_summary <- rotated_dr_summary %>%
  group_by(exp, ppid) %>%
  summarise(
    rate_of_change_means = slope(miniblock_num, means),
    rate_of_change_slopes = slope(miniblock_num, slopes),
    rate_of_change_intercepts = slope(miniblock_num, intercepts)
  )

# third order summary
rotated_dr_exp_summary <- rotated_dr_2nd_order_summary %>%
  group_by(exp) %>%
  summarise(
    mean_rate_of_change_means = mean(rate_of_change_means),
    means_cis = vector_confint(rate_of_change_means),
    mean_rate_of_change_slopes = mean(rate_of_change_slopes),
    slopes_cis = vector_confint(rate_of_change_slopes),
    mean_rate_of_change_intercepts = mean(rate_of_change_intercepts),
    intercepts_cis = vector_confint(rate_of_change_intercepts)
  )
```


```{r}
# plot slopes
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = slopes, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Slope of Angle Change On Shape Switch", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/switch_block_slopes.png", f, width = 30, height = 20)

f
```

```{r}
# plot intercepts
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = intercepts, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Intercept of Angle Change On Shape Switch", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/switch_block_intercepts.png", f, width = 30, height = 20)

f
```

```{r}
# plot means
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = means, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Mean Angle Change On Shape Switch", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/switch_block_means.png", f, width = 30, height = 20)

f
```

```{r}
# plot rate of change of means using beeswarm
f <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_means, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_means), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_means, ymin = mean_rate_of_change_means - means_cis, ymax = mean_rate_of_change_means + means_cis), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Mean Angle Change On Shape Switch", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/switch_block_means_rate_of_change.png", f, width = 30, height = 20)

f
```

```{r}
# plot rate of change of slopes using beeswarm
f <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_slopes, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_slopes), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_slopes, ymin = mean_rate_of_change_slopes - slopes_cis, ymax = mean_rate_of_change_slopes + slopes_cis), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Slope of Angle Change On Shape Switch", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/switch_block_slopes_rate_of_change.png", f, width = 30, height = 20)

f
```

```{r}
# plot rate of change of intercepts using beeswarm
f <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_intercepts, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_intercepts), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_intercepts, ymin = mean_rate_of_change_intercepts - intercepts_cis, ymax = mean_rate_of_change_intercepts + intercepts_cis), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Intercept of Angle Change On Shape Switch", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/switch_block_intercepts_rate_of_change.png", f, width = 30, height = 20)

f
```
### Changes to first trial after rotation-switch over time
```{r}
# isolate only the dr_30 and dr_60 data
rotated_dr <- all_data %>%
  filter(
    exp %in% c("dr_30", "dr_60"),
    type == "reach", dual_rotation != 0
  )

# summarise
rotated_dr_summary <- rotated_dr %>%
  group_by(exp, ppid, miniblock_num, obj_shape_sign) %>%
  summarise(
    first_switch_trial = first(obj_angle_3cm_move),
    mean_second_2_switch_trials = mean(obj_angle_3cm_move[2:3]),
    rate_second_2_switch_trials = slope(1:2, obj_angle_3cm_move[2:3]),
    intercept_second_2_switch_trials = intercept(1:2, obj_angle_3cm_move[2:3], slope(1:2, obj_angle_3cm_move[2:3]))
  )


# multiply slopes and intercepts by obj_shape_sign
rotated_dr_summary <- rotated_dr_summary %>%
  mutate(
    first_switch_trial = first_switch_trial * obj_shape_sign,
    mean_second_2_switch_trials = mean_second_2_switch_trials * obj_shape_sign,
    rate_second_2_switch_trials = rate_second_2_switch_trials * obj_shape_sign,
    intercept_second_2_switch_trials = intercept_second_2_switch_trials * obj_shape_sign
  )


# make second order summary
rotated_dr_2nd_order_summary <- rotated_dr_summary %>%
  group_by(exp, ppid) %>%
  summarise(
    rate_of_change_first_switch = slope(miniblock_num, first_switch_trial),
    rate_of_change_2_means = slope(miniblock_num, mean_second_2_switch_trials),
    rate_of_change_2_rate = slope(miniblock_num, rate_second_2_switch_trials),
    rate_of_change_2_intercept = slope(miniblock_num, intercept_second_2_switch_trials)
  )

# third order summary
rotated_dr_exp_summary <- rotated_dr_2nd_order_summary %>%
  group_by(exp) %>%
  summarise(
    mean_rate_of_change_first_switch = mean(rate_of_change_first_switch),
    ci_rate_of_change_first_switch = vector_confint(rate_of_change_first_switch),
    mean_rate_of_change_2_means = mean(rate_of_change_2_means),
    ci_rate_of_change_2_means = vector_confint(rate_of_change_2_means),
    mean_rate_of_change_2_rate = mean(rate_of_change_2_rate),
    ci_rate_of_change_2_rate = vector_confint(rate_of_change_2_rate),
    mean_rate_of_change_2_intercept = mean(rate_of_change_2_intercept),
    ci_rate_of_change_2_intercept = vector_confint(rate_of_change_2_intercept)
  )
```
```{r}
# plot first trial after switch
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = first_switch_trial, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Hand-Angle on First Switch Trial", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/first_switch.png", f, width = 15, height = 10)

f

# plot summary of first trial after switch
f2 <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_first_switch, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_first_switch), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_first_switch, ymin = mean_rate_of_change_first_switch - ci_rate_of_change_first_switch, ymax = mean_rate_of_change_first_switch + ci_rate_of_change_first_switch), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Hand-Angle on First Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/first_switch_summary.png", f2, width = 15, height = 10)

f2
```
```{r}
# plot mean of second and third trials after switch
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = mean_second_2_switch_trials, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Mean Hand-Angle on Second and Third Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/second2_switch_mean.png", f, width = 15, height = 10)

f

# plot summary of mean of second and third trials after switch
f2 <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_2_means, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_2_means), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_2_means, ymin = mean_rate_of_change_2_means - ci_rate_of_change_2_means, ymax = mean_rate_of_change_2_means + ci_rate_of_change_2_means), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Mean Hand-Angle on Second and Third Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/second2_switch_mean_summary.png", f2, width = 15, height = 10)

f2
```
```{r}
# plot rate of change of second and third trials after switch
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = rate_second_2_switch_trials, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Rate of Change of Hand-Angle on Second and Third Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/second2_switch_rate.png", f, width = 15, height = 10)

f

# plot summary of rate of change of second and third trials after switch
f2 <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_2_rate, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_2_rate), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_2_rate, ymin = mean_rate_of_change_2_rate - ci_rate_of_change_2_rate, ymax = mean_rate_of_change_2_rate + ci_rate_of_change_2_rate), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Rate of Change of Hand-Angle on Second and Third Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/second2_switch_rate_summary.png", f2, width = 15, height = 10)

f2
```
```{r}
# plot intercept of second and third trials after switch
f <- rotated_dr_summary %>%
  ggplot(aes(x = miniblock_num, y = intercept_second_2_switch_trials, colour = ppid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~exp) +
  labs(x = "Miniblock Number", y = "Intercept of Hand-Angle on Second and Third Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/second2_switch_intercept.png", f, width = 15, height = 10)

f

# plot summary of intercept of second and third trials after switch
f2 <- rotated_dr_2nd_order_summary %>%
  ggplot(aes(x = exp, y = rate_of_change_2_intercept, colour = ppid)) +
  geom_beeswarm() +
  geom_point(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_2_intercept), size = 3, colour = "red") +
  geom_errorbar(data = rotated_dr_exp_summary, aes(x = exp, y = mean_rate_of_change_2_intercept, ymin = mean_rate_of_change_2_intercept - ci_rate_of_change_2_intercept, ymax = mean_rate_of_change_2_intercept + ci_rate_of_change_2_intercept), width = 0.2, colour = "red") +
  labs(x = "Experiment", y = "Rate of Change of Intercept of Hand-Angle on Second and Third Switch Trials", colour = "Participant") +
  theme(legend.position = "none")

# save plot
ggsave("../plots/second2_switch_intercept_summary.png", f2, width = 15, height = 10)

f2
```



Stats for the above plot

```{r}
# Fin
```

