---
title: "Supplementary Data Analysis"
author: "Shanaa Modchalingam"
date: '2023'
output: 
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE, warning=FALSE}
rm(list = ls()) # clean environment

source("../src/helper_funcs.R")
library(data.table)
library(tidyverse)
library(future) # for parallel processing
library(collections)
library(ggbeeswarm)

library(ez) # for ANOVAs NOTE:ez THE afex PACKAGE IS A LOT BETTER FOR POSTHOC TESTS
library(afex) # for ANOVAs
library(emmeans)
library(effectsize) # for eta-squared
library(BayesFactor)
library(bayestestR)

library(Reach) # from github: thartbm/Reach
library(dabestr)

# Helper functions
##### Helper functions #####
slope <- function(x, y) {
  return(cov(x, y) / var(x))
}

intercept <- function(x, y, slope) {
  b <- mean(y) - (slope * mean(x))
  return(b)
}

# settings
save_plots <- FALSE
```

# Data Import and Cleaning
```{r}
# import data
data_path <- "../data/preprocessed/omnibus/omnibus_bl_corrected.csv"

all_data <- fread(data_path)

## Setup ##
palette <- dict(
  list(
    "s30" = "#a30f15",
    "d30" = "#07509b",
    "s30-a" = "#fb6949",
    "d30-a" = "#6aafd2",
    "a-1" = "#4f1b31",
    "a-2" = "#d6819b"
  )
)

## Isolate experiments and summarize ##
sr_30_all <- all_data %>%
  filter(exp == "sr_30") %>%
  mutate(unsigned_obj_angle = obj_angle_3cm_move * obj_shape_sign * -1) %>%
  mutate(unsigned_hand_angle = hand_angle_3cm_move * obj_shape_sign * -1)

sr_30_ppt_training <- sr_30_all %>%
  filter(block_num == 16) %>%
  mutate(trial_set = case_when(
    trial_num <= 141 ~ 1,
    trial_num >= 310 ~ 2,
    TRUE ~ 100
  ))

sr_30_clamped <- sr_30_all %>%
  filter(block_num > 16, type == "clamped") %>%
  mutate(trained_obj_factor = case_when(
    trainedfirst_obj_shape == obj_shape ~ "trained_obj",
    TRUE ~ "untrained_obj"
  )) %>%
  mutate(trained_hand_factor = case_when(
    hand == "r" ~ "trained_hand",
    TRUE ~ "untrained_hand"
  )) %>%
  mutate(trained_obj_hand_factor = paste0(trained_obj_factor, "_", trained_hand_factor))

### DR 30 ###
dr_30_all <- all_data %>%
  filter(exp == "dr_30") %>%
  mutate(unsigned_obj_angle = obj_angle_3cm_move * obj_shape_sign * -1) %>%
  mutate(unsigned_hand_angle = hand_angle_3cm_move * obj_shape_sign * -1)

dr_30_ppt_training <- dr_30_all %>%
  filter(block_num == 7) %>%
  mutate(trial_set = case_when(
    trial_num <= 78 ~ 1,
    trial_num >= 247 ~ 2,
    TRUE ~ 100
  ))

# note: blocks 8 and 11 are include clamps, 13 is exclude clamps
dr_30_incl_clamp <- dr_30_all %>%
  filter(block_num %in% c(8, 11))

dr_30_excl_clamp <- dr_30_all %>%
  filter(block_num %in% c(13, 14))

# both experiment rbind
both_ppt_training <- rbind(sr_30_ppt_training, dr_30_ppt_training)
``` 

# Single Learning
## Training Phase Trial Sets - Reach Step
```{r}
sr_30_ppt_trial_sets <- sr_30_ppt_training %>%
  filter(trial_set < 5) %>%
  group_by(ppid, trial_set, targetAngle) %>%
  summarise(
    mean_trial_set_angle = mean(unsigned_hand_angle),
    n()
  )

sr_30_ppt_trial_sets$ppid <- as.factor(sr_30_ppt_trial_sets$ppid)
sr_30_ppt_trial_sets$trial_set <- as.factor(sr_30_ppt_trial_sets$trial_set)
sr_30_ppt_trial_sets$targetAngle <- as.factor(sr_30_ppt_trial_sets$targetAngle)

sr_30_trial_set_devs <- sr_30_ppt_trial_sets %>%
  group_by(trial_set, targetAngle) %>%
  summarise(
    trial_set_mean = mean(mean_trial_set_angle),
    trial_set_ci = vector_confint(mean_trial_set_angle)
  )

data_ppt <- sr_30_ppt_trial_sets
data_trial_set <- sr_30_trial_set_devs

# set up plot
p <- data_trial_set %>%
  ggplot(
    aes(
      x = trial_set, y = trial_set_mean
    )
  ) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(
    x = NULL,
    y = "Hand Angle (°)"
  )

# add horizontal lines
p <- p +
  geom_hline(
    yintercept = c(0, 30), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "solid"
  ) +
  geom_hline(
    yintercept = c(15), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "dashed"
  )

# add axis ticks
p <- p +
  scale_y_continuous(
    limits = c(-15, 40),
    breaks = c(0, 15, 30),
    labels = c(0, 15, 30)
  )

# set font size to 11
p <- p +
  theme(text = element_text(size = 11))

# add data points
p <- p +
  geom_beeswarm(
    data = data_ppt,
    aes(y = mean_trial_set_angle, colour = targetAngle),
    alpha = 0.5,
    size = 1
  ) +
  geom_linerange(aes(
    ymin = trial_set_mean - trial_set_ci,
    ymax = trial_set_mean + trial_set_ci
  ), alpha = 0.1, lwd = 2) +
  geom_point()

# p <- p +
#   scale_color_manual(
#     values = c(
#       "#555555", "#555555"
#     )
#   )

p <- p +
  scale_x_discrete(
    labels = c(
      "Init\nT", "Fin\nT"
    )
  )

p
```


```{r}
# ANOVA using afex (identical values to ez but ez doesn't remove missing rows)
(temp_ANOVA <- aov_car(mean_trial_set_angle ~ targetAngle * trial_set + Error(ppid / (targetAngle * trial_set)), data_ppt))

bf <- anovaBF(mean_trial_set_angle ~ targetAngle * trial_set + ppid,
  data = data.frame(data_ppt), whichRandom = "ppid", progress = FALSE
)
print(bf)
bayesfactor_inclusion(bf)
```

## Training Phase Trial Sets - Transport Step
```{r}
sr_30_ppt_trial_sets <- sr_30_ppt_training %>%
  filter(trial_set < 5) %>%
  group_by(ppid, trial_set, targetAngle) %>%
  summarise(
    mean_trial_set_angle = mean(unsigned_obj_angle)
  )

sr_30_ppt_trial_sets$ppid <- as.factor(sr_30_ppt_trial_sets$ppid)
sr_30_ppt_trial_sets$trial_set <- as.factor(sr_30_ppt_trial_sets$trial_set)
sr_30_ppt_trial_sets$targetAngle <- as.factor(sr_30_ppt_trial_sets$targetAngle)

sr_30_trial_set_devs <- sr_30_ppt_trial_sets %>%
  group_by(trial_set, targetAngle) %>%
  summarise(
    trial_set_mean = mean(mean_trial_set_angle),
    trial_set_ci = vector_confint(mean_trial_set_angle)
  )

data_ppt <- sr_30_ppt_trial_sets
data_trial_set <- sr_30_trial_set_devs

# set up plot
p <- data_trial_set %>%
  ggplot(
    aes(
      x = trial_set, y = trial_set_mean
    )
  ) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(
    x = NULL,
    y = NULL
  )

# add horizontal lines
p <- p +
  geom_hline(
    yintercept = c(0, 30), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "solid"
  ) +
  geom_hline(
    yintercept = c(15), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "dashed"
  )

# add axis ticks
p <- p +
  scale_y_continuous(
    limits = c(-15, 40),
    breaks = c(0, 15, 30),
    labels = c(0, 15, 30)
  )

# set font size to 11
p <- p +
  theme(text = element_text(size = 11))

# add data points
p <- p +
  geom_beeswarm(
    data = data_ppt,
    aes(y = mean_trial_set_angle, colour = targetAngle),
    alpha = 0.5,
    size = 1
  ) +
  geom_linerange(aes(
    ymin = trial_set_mean - trial_set_ci,
    ymax = trial_set_mean + trial_set_ci
  ), alpha = 0.1, lwd = 2) +
  geom_point()

# p <- p +
#   scale_color_manual(
#     values = c(
#       palette$get("s30"), palette$get("s30")
#     )
#   )

p <- p +
  scale_x_discrete(
    labels = c(
      "Init\nT", "Fin\nT"
    )
  )

p
```


```{r}
# ANOVA using afex (identical values to ez but ez doesn't remove missing rows)
(temp_ANOVA <- aov_car(mean_trial_set_angle ~ targetAngle * trial_set + Error(ppid / (targetAngle * trial_set)), data_ppt))

bf <- anovaBF(mean_trial_set_angle ~ targetAngle * trial_set + ppid,
  data = data.frame(data_ppt), whichRandom = "ppid", progress = FALSE
)
print(bf)
bayesfactor_inclusion(bf)
```

No effects of target Angle (BFincl of 0.04 and 0.08)

# Dual Learning Experiment
## Training Phase Trial Sets - Reach Step
```{r}
dr_30_ppt_trial_sets <- dr_30_ppt_training %>%
  filter(trial_set < 5) %>%
  group_by(ppid, trial_set, targetAngle) %>%
  summarise(
    mean_trial_set_angle = mean(unsigned_hand_angle)
  )

dr_30_ppt_trial_sets$ppid <- as.factor(dr_30_ppt_trial_sets$ppid)
dr_30_ppt_trial_sets$trial_set <- as.factor(dr_30_ppt_trial_sets$trial_set)
dr_30_ppt_trial_sets$targetAngle <- as.factor(dr_30_ppt_trial_sets$targetAngle)

dr_30_trial_set_devs <- dr_30_ppt_trial_sets %>%
  group_by(trial_set, targetAngle) %>%
  summarise(
    trial_set_mean = mean(mean_trial_set_angle),
    trial_set_ci = vector_confint(mean_trial_set_angle)
  )

data_ppt <- dr_30_ppt_trial_sets
data_trial_set <- dr_30_trial_set_devs

# set up plot
p <- data_trial_set %>%
  ggplot(
    aes(
      x = trial_set, y = trial_set_mean,
      color = trial_set
    )
  ) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(
    x = NULL,
    y = "Hand Angle (°)"
  )

# add horizontal lines
p <- p +
  geom_hline(
    yintercept = c(-30, 0, 30), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "solid"
  ) +
  geom_hline(
    yintercept = c(-15, 15), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "dashed"
  )

# add axis ticks
p <- p +
  scale_y_continuous(
    limits = c(-30, 30),
    breaks = c(-30, -15, 0, 15, 30),
    labels = c(-30, -15, 0, 15, 30)
  )

# set font size to 11
p <- p +
  theme(text = element_text(size = 11))

# add data points
p <- p +
  geom_beeswarm(
    data = data_ppt,
    aes(y = mean_trial_set_angle, colour = targetAngle),
    alpha = 0.5,
    size = 1
  ) +
  geom_linerange(aes(
    ymin = trial_set_mean - trial_set_ci,
    ymax = trial_set_mean + trial_set_ci
  ), alpha = 0.1, lwd = 2) +
  geom_point()

# p <- p +
#   scale_color_manual(
#     values = c(
#       "#555555", "#555555"
#     )
#   )

p <- p +
  scale_x_discrete(
    labels = c(
      "Init", "Fin"
    )
  )

p
```

```{r}
# ANOVA using afex (identical values to ez but ez doesn't remove missing rows)
(temp_ANOVA <- aov_car(mean_trial_set_angle ~ targetAngle * trial_set + Error(ppid / (targetAngle * trial_set)), data_ppt))

bf <- anovaBF(mean_trial_set_angle ~ targetAngle * trial_set + ppid,
  data = data.frame(data_ppt), whichRandom = "ppid", progress = FALSE
)
print(bf)
bayesfactor_inclusion(bf)
```
## Training Phase Trial Sets - Transport Step
```{r}
dr_30_ppt_trial_sets <- dr_30_ppt_training %>%
  filter(trial_set < 5) %>%
  group_by(ppid, trial_set, targetAngle) %>%
  summarise(
    mean_trial_set_angle = mean(unsigned_obj_angle)
  )

dr_30_ppt_trial_sets$ppid <- as.factor(dr_30_ppt_trial_sets$ppid)
dr_30_ppt_trial_sets$trial_set <- as.factor(dr_30_ppt_trial_sets$trial_set)
dr_30_ppt_trial_sets$targetAngle <- as.factor(dr_30_ppt_trial_sets$targetAngle)

dr_30_trial_set_devs <- dr_30_ppt_trial_sets %>%
  group_by(trial_set, targetAngle) %>%
  summarise(
    trial_set_mean = mean(mean_trial_set_angle),
    trial_set_ci = vector_confint(mean_trial_set_angle)
  )

data_ppt <- dr_30_ppt_trial_sets
data_trial_set <- dr_30_trial_set_devs

# set up plot
p <- data_trial_set %>%
  ggplot(
    aes(
      x = trial_set, y = trial_set_mean
    )
  ) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(
    x = NULL,
    y = NULL
  )

# add horizontal lines
p <- p +
  geom_hline(
    yintercept = c(0, 30), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "solid"
  ) +
  geom_hline(
    yintercept = c(15), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "dashed"
  )

# add axis ticks
p <- p +
  scale_y_continuous(
    limits = c(-15, 40),
    breaks = c(0, 15, 30),
    labels = c(0, 15, 30)
  )

# set font size to 11
p <- p +
  theme(text = element_text(size = 11))

# add data points
p <- p +
  geom_beeswarm(
    data = data_ppt,
    aes(y = mean_trial_set_angle, colour = targetAngle),
    alpha = 0.5,
    size = 1
  ) +
  geom_linerange(aes(
    ymin = trial_set_mean - trial_set_ci,
    ymax = trial_set_mean + trial_set_ci
  ), alpha = 0.1, lwd = 2) +
  geom_point()

# p <- p +
#   scale_color_manual(
#     values = c(
#       palette$get("s30"), palette$get("s30")
#     )
#   )

p <- p +
  scale_x_discrete(
    labels = c(
      "Init\nT", "Fin\nT"
    )
  )

p
```


```{r}
# ANOVA using afex (identical values to ez but ez doesn't remove missing rows)
(temp_ANOVA <- aov_car(mean_trial_set_angle ~ targetAngle * trial_set + Error(ppid / (targetAngle * trial_set)), data_ppt))

bf <- anovaBF(mean_trial_set_angle ~ targetAngle * trial_set + ppid,
  data = data.frame(data_ppt), whichRandom = "ppid", progress = FALSE
)
print(bf)
bayesfactor_inclusion(bf)
```


No effect of target angle (BFinc = 0.07, 0.14)


## Clamped Tasks
### Not excluding strategy
```{r}
dr_30_ppt_incl_clamped <- dr_30_incl_clamp %>%
  group_by(ppid, obj_shape_sign, targetAngle) %>%
  summarise(
    ppt_mean_angle = mean(obj_angle_3cm_move),
    ppt_ci_angle = vector_confint(obj_angle_3cm_move)
  )

dr_30_ppt_incl_clamped$ppid <- factor(dr_30_ppt_incl_clamped$ppid)
dr_30_ppt_incl_clamped$obj_shape_sign <- factor(dr_30_ppt_incl_clamped$obj_shape_sign)
dr_30_ppt_incl_clamped$targetAngle <- factor(dr_30_ppt_incl_clamped$targetAngle)

dr_30_exp_incl_clamped <- dr_30_ppt_incl_clamped %>%
  group_by(obj_shape_sign, targetAngle) %>%
  summarise(
    mean_angle = mean(ppt_mean_angle),
    ci_angle = vector_confint(ppt_mean_angle)
  )

data_ppt <- dr_30_ppt_incl_clamped
data_exp <- dr_30_exp_incl_clamped

# set up plot
p <- data_exp %>%
  ggplot(
    aes(
      x = obj_shape_sign,
      y = mean_angle,
      color = obj_shape_sign,
      shape = targetAngle
    )
  ) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(
    x = NULL,
    y = NULL
  )

# add horizontal lines
p <- p +
  geom_hline(
    yintercept = c(-30, 0, 30), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "solid"
  ) +
  geom_hline(
    yintercept = c(-15, 15), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "dashed"
  )

# add axis ticks
p <- p +
  scale_y_continuous(
    limits = c(-30, 30),
    breaks = c(-30, -15, 0, 15, 30),
    labels = c(-30, -15, 0, 15, 30)
  )

p <- p +
  scale_x_discrete(
    labels = c(
      "CW", "CCW"
    )
  )

# set font size to 11
p <- p +
  theme(text = element_text(size = 11))

# add data points
p <- p +
  geom_beeswarm(
    data = data_ppt,
    aes(
      x = obj_shape_sign,
      y = ppt_mean_angle,
      color = obj_shape_sign,
      shape = targetAngle
    ),
    size = 1,
    alpha = 0.2
  ) +
  geom_linerange(
    aes(
      ymin = mean_angle - ci_angle,
      ymax = mean_angle + ci_angle
    ),
    alpha = 0.5, lwd = 2
  ) +
  geom_point()

p <- p +
  scale_color_manual(
    values = c(palette$get("a-1"), palette$get("a-2"))
  )

p
```

```{r}
# summary statistics
data_ppt %>%
  group_by(obj_shape_sign, targetAngle) %>%
  summarise(
    mean = mean(ppt_mean_angle),
    ci = vector_confint(ppt_mean_angle),
    n = n()
  )
```

```{r}
# ANOVA using afex (identical values to ez but ez doesn't remove missing rows)
(temp_ANOVA <- aov_car(ppt_mean_angle ~ targetAngle * obj_shape_sign + Error(ppid / (targetAngle * obj_shape_sign)), data_ppt))

bf <- anovaBF(ppt_mean_angle ~ targetAngle * obj_shape_sign + ppid,
  data = data.frame(data_ppt), whichRandom = "ppid", progress = FALSE
)
print(bf)
bayesfactor_inclusion(bf)
```


### Exclude strategy reaches
```{r}
dr_30_ppt_excl_clamped <- dr_30_excl_clamp %>%
  group_by(ppid, obj_shape_sign, targetAngle) %>%
  summarise(
    ppt_mean_angle = mean(obj_angle_3cm_move),
    ppt_ci_angle = vector_confint(obj_angle_3cm_move)
  )

dr_30_ppt_excl_clamped$ppid <- factor(dr_30_ppt_excl_clamped$ppid)
dr_30_ppt_excl_clamped$obj_shape_sign <- factor(dr_30_ppt_excl_clamped$obj_shape_sign)
dr_30_ppt_excl_clamped$targetAngle <- factor(dr_30_ppt_excl_clamped$targetAngle)

dr_30_exp_excl_clamped <- dr_30_ppt_excl_clamped %>%
  group_by(obj_shape_sign, targetAngle) %>%
  summarise(
    mean_angle = mean(ppt_mean_angle),
    ci_angle = vector_confint(ppt_mean_angle)
  )

data_ppt <- dr_30_ppt_excl_clamped
data_exp <- dr_30_exp_excl_clamped

# set up plot
p <- data_exp %>%
  ggplot(
    aes(
      x = obj_shape_sign,
      y = mean_angle,
      color = obj_shape_sign,
      shape = targetAngle
    )
  ) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(
    x = NULL,
    y = NULL
  )

# add horizontal lines
p <- p +
  geom_hline(
    yintercept = c(-30, 0, 30), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "solid"
  ) +
  geom_hline(
    yintercept = c(-15, 15), linewidth = 0.4,
    colour = "#CCCCCC", linetype = "dashed"
  )

# add axis ticks
p <- p +
  scale_y_continuous(
    limits = c(-30, 30),
    breaks = c(-30, -15, 0, 15, 30),
    labels = c(-30, -15, 0, 15, 30)
  )

p <- p +
  scale_x_discrete(
    labels = c(
      "CW", "CCW"
    )
  )

# set font size to 11
p <- p +
  theme(text = element_text(size = 11))

# add data points
p <- p +
  geom_beeswarm(
    data = data_ppt,
    aes(
      x = obj_shape_sign,
      y = ppt_mean_angle,
      color = obj_shape_sign,
      shape = targetAngle
    ),
    size = 1,
    alpha = 0.2
  ) +
  geom_linerange(
    aes(
      ymin = mean_angle - ci_angle,
      ymax = mean_angle + ci_angle
    ),
    alpha = 0.5, lwd = 2
  ) +
  geom_point()

p <- p +
  scale_color_manual(
    values = c(palette$get("a-1"), palette$get("a-2"))
  )

p
```

```{r}
# summary statistics
data_ppt %>%
  group_by(obj_shape_sign, targetAngle) %>%
  summarise(
    mean = mean(ppt_mean_angle),
    ci = vector_confint(ppt_mean_angle),
    n = n()
  )
```

```{r}
# ANOVA using afex (identical values to ez but ez doesn't remove missing rows)
(temp_ANOVA <- aov_car(ppt_mean_angle ~ targetAngle * obj_shape_sign + Error(ppid / (targetAngle * obj_shape_sign)), data_ppt))

bf <- anovaBF(ppt_mean_angle ~ targetAngle * obj_shape_sign + ppid,
  data = data.frame(data_ppt), whichRandom = "ppid", progress = FALSE
)
print(bf)
bayesfactor_inclusion(bf)
```
```{r}
# posthoc tests
(m1 <- emmeans(temp_ANOVA, ~ targetAngle * obj_shape_sign))
pairs(m1)
```
